---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Results {-}

```{r results, echo=F, message=F, warning=F}
  # Use pandoc for Word documents
  format="pandoc"

knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = F, fig.align = 'center', out.width = '90%', fig.width = 10)

library(bookdown)
library(tidyverse)
library(lubridate)
library(tableone)
library(readxl)
library(yardstick)


questions <- readRDS('data/orig_col_names.rds')

df <- readRDS('data/df.rds') %>%
  mutate_at(vars(starts_with("freq_fall_"), "prop_non_convey_diff_meds"), as.numeric) %>%
  # Tidy up some values and combine others with
  # small values
  mutate(
    role = case_when(
      role %in% c("cdm", "clinical supervisor", "consultant paramedic", "locality manager", "manager", "frequent caller case officer") ~ "manager",
    grepl("student", role) ~ "student paramedic",
    role %in% c("eca", "emergency care assistant") ~ "emergency care assistant",
    TRUE ~ role
    ),
    cmr_refer = case_when(
      grepl("know", cmr_refer) ~ "unsure",
      TRUE ~ cmr_refer
    ),
    cmr_yes_no = ifelse(grepl("yes", cmr_refer), "yes", "no/unsure"),
    # Sort cmr referral importance as factor
    imp_cmr_refer_option = ordered(imp_cmr_refer_option, levels = c("very important", "important", "neutral", "unimportant", "very unimportant")),
    freq_falls_over65 = factor(freq_falls_over65, levels = c("more than once a shift", "once a shift", "once a week", "once a month")),
  )


df1 <- df %>%
  rename(
    `respondent role` = role,
    `full-time/part-time` = freq_ops,
    # Note use of bang-bang and :=
    !!questions[4]  := freq_falls_over65,
    !!questions[5]  := freq_fall_nonconvey,
    !!questions[6]  := freq_fall_refer,
    !!questions[7]  := freq_fall_gp,
    !!questions[13] := prop_non_convey_diff_meds,
    !!questions[15] := cmr_refer,
    !!questions[16] := imp_cmr_refer_option
  )

vars <- df1 %>% select("respondent role", "full-time/part-time",  questions[4:7], questions[c(13,15:16)]) %>% colnames()

summary_table <- CreateTableOne(
  vars = vars,
  strata = "cmr_yes_no",
  data = df1,
  test = F,
  factorVars = c("respondent role", "full-time/part-time", questions[4],  questions[15], questions[16]),
  includeNA = T,
  addOverall = T
)

nonnormal <- questions[c(4:7,13)]

cmr_summary = df1 %>% count(cmr_yes_no)


# Process free text response coding


struggle_df <- df %>%
  dplyr::select(starts_with("struggle_theme")) %>%
  mutate(
    id = row_number()
  ) %>%
  pivot_longer(cols = starts_with("struggle"), 
               names_to=c("rank", "person"), 
               names_pattern = "struggle_theme_?(.*)\\.(.*)",
               values_to = "theme") %>%
  filter(!is.na(theme)) %>%
  group_by(id) %>%
  summarise(
    "observation of living situation" = sum(theme == "observation of living situation"),
    "observation of patient" = sum(theme == "observation of patient"),
    "patient / carer discussion / disclosure" = sum(theme == "patient / carer discussion / disclosure"),
    "patient clinical presentation" = sum(theme == "patient clinical presentation"),
  ) %>%
  pivot_longer(cols = -id, names_to = "theme", values_to = "value") %>%
  filter(value == 2) %>%
  count(theme, sort = T)

care_df <- df %>%
  dplyr::select(starts_with("care_plan_theme")) %>%
  mutate(
    id = row_number()
  ) %>%
  pivot_longer(cols = starts_with("care"), 
               names_to=c("rank", "person"), 
               names_pattern = "care_plan_theme_?(.*)\\.(.*)",
               values_to = "theme") %>%
  filter(!is.na(theme)) %>%
  group_by(id) %>%
  summarise(
    "discuss and confirm" = sum(theme == "discuss and confirm"),
    "immediate mitigation" = sum(theme == "immediate mitigation"),
    "referral" = sum(theme == "referral"),
    "safety net" = sum(theme == "safety net"),
  ) %>%
  pivot_longer(cols = -id, names_to = "theme", values_to = "value") %>%
  filter(value == 2) %>%
  count(theme, sort = T)

```

There were `r df1 %>% count() %>% pull(n)` responses to the survey, including `r cmr_summary$n[2]`/`r df1 %>% count() %>% pull(n)` (`r round((cmr_summary$n[2]/df1 %>% count() %>% pull(n))*100, 1)`%) from clinicians who had made a CMR referral (Table \@ref(tab:summarytable)). The majority of respondents were full-time, a paramedic and attended 1 or more fall-related calls per shift. Responses to most questions were similar between respondents who had made a CMR referral and those who had not, with the exception that CMR referral respondents perceived a higher proportion of patients who were not conveyed after a fall having difficulty with their medicines (50% vs 40%). Both groups had a high number of respondents who reported having an option to make a CMR referral being important or very important (88.9% and 85.1% for CMR referral and non-CMR referral groups respectively).



```{r summarytable}

kableone(print(summary_table, showAllLevels = T, nonnormal = nonnormal), format = format, caption = "Summary of survey responses")

```


The risk factors identifying patients having difficulty managing their medicines with the highest weighted mean scores, as voted by respodnents, were patients stating that they were not taking their medicines as prescribed and the presence of unused medicines around the home (Table \@ref(tab:rank-score)). These results were also reflected in the free-text responses (Table \@ref(tab:code-struggle)) relating to identification of patients having difficult with their medicines. Participant responses fell into one or more of four categories:

+ Observation of living situation e.g. stockpiled drugs, tablets on floor, chaotic lifestyle, self-neglect
+ Patient/carer discussion/disclosure e.g. unsure when to take medicine, patients stating that they are not taking medicines, family/carer concern
+ Patient clinical presentation e.g. memory problems, accidental overdose, physiological observations characterising poor management of medicated condition, polypharmacy
+ Observation of patient e.g. patient unable to open medicines packaging, difficulty in swallowing medicines, muddles inhalers.

```{r rank}

rank_df <- df %>%
  select(id, risk_factors_diff_meds) %>%
  # Split character vector into list and then put each row of the list on a new dataframe row
  unnest(y = str_split(risk_factors_diff_meds, "\r\n\\s?", simplify = F)) %>% select(id, y) %>%
  # Separate the number (rank) from the risk factor (item)
  separate(col="y", into=c("rank", "item"), sep = "(?<=[\\d+])\\s?") %>%
  filter(
    # Only going to look at top 5 since likely people got bored after
    # dragging and dropping 5 risk factors around the screen
    rank <= 5,
    # Rank 10 was split into 1 and 0. Not a problem since not including it, but it needs removing
    item != 0
  ) %>%
  mutate(
    item = str_replace(item, "\\r?\\s?\\d+", ""),
    item = ifelse(grepl("can", item), "patient cannot recall all their prescribed medicines", item)
  )

totals_df <- rank_df %>%
  count(item, rank) %>%
  group_by(item) %>%
  summarise(
    tot_n = sum(n),
    rank1 = sum(n[rank == "1"], na.rm = T),
    rank2 = sum(n[rank == "2"], na.rm = T),
    rank3 = sum(n[rank == "3"], na.rm = T),
    rank4 = sum(n[rank == "4"], na.rm = T),
    rank5 = sum(n[rank == "5"], na.rm = T),
    total = 5*first(n[rank == "1"], default = 0) + 4*first(n[rank == "2"], default = 0) + 3*first(n[rank == "3"], default = 0) + 2*first(n[rank == "4"], default = 0) + first(n[rank == "5"], default = 0),
    wght_mean = round(total/tot_n,1)
  ) %>%
  arrange(desc(wght_mean)) %>%
  select(-total) %>%
  select(item, rank1, rank2, rank3, rank4, rank5, tot_n, wght_mean)

colnames(totals_df) <- c("Risk factor",  "1st", "2nd", "3rd", "4th", "5th","total number of responses", "weighted mean")


```


```{r rank-score}

knitr::kable(totals_df, caption = "Risk factors for patients having difficulty managing their medication ordered by weight mean", format = format)

```

```{r}

library(MASS)

df2 <- df %>%
  dplyr::select(role, freq_ops, cmr_yes_no, imp_cmr_refer_option, freq_falls_over65, freq_fall_refer) %>%
  mutate(paramedic = ifelse(grepl("paramedic", role), 1, 0))

#fit <- polr(imp_cmr_refer_option ~ paramedic + freq_ops, data = df2)

fit <- polr(imp_cmr_refer_option ~ relevel(as.factor(role), ref = "paramedic") + freq_ops, data = df2, Hess = T)

olr_result <- tidy(fit, exponentiate = T, conf.int = T, p.values = T)

olr_res2 <- olr_result %>% 
   mutate_if(is.double, round,2) %>% 
  filter(coef.type == "coefficient") %>% 
  mutate(
    `95% CI` = paste0(conf.low,"--", conf.high),
    term = case_when(
      # https://stackoverflow.com/questions/3872070/how-to-force-r-to-use-a-specified-factor-level-as-reference-in-a-regression
      #https://stackoverflow.com/a/32767436/3650230
      
      grepl("relevel", term) ~ gsub(".*?)", "", str_replace(term, " \\(.*\\)", "")),
      TRUE ~ str_replace(term, "freq_ops", "")
    )
  ) %>%
  dplyr::select(term, estimate, `95% CI`)



#coeffs <- coef(summary(fit))
#p <- pnorm(abs(coeffs[,"t value"]), lower.tail = F) * 2

#cbind(coeffs, "p value" = round(p, 3))

```



```{r code-struggle}

knitr::kable(struggle_df, caption = "Themes arising from free-text responses relating to respondents identifying a patient having difficulty with their medication", format = format)

```




There was no apparent relationship between respondent's current role or frequency of operational duties and their value of a CMR referral pathway (Table \@ref(tab:role-cmr)).

```{r role-cmr }

knitr::kable(olr_res2, caption = "Ordinal regression model between reported importance of CMR referral and respondent role and frequency of operational duties")

```


Finally, care planning for patients perceived by clinicians having difficulty managing their medicines were categorised into four themes (Table \@ref(tab:code-plan)):

+ Referral e.g. CMR, GP, fall pathway
+ Discuss and confirm e.g. review of medical records, confirmation of situation with carer/family/other healthcare professionals
+ Immediate mitigation e.g. arranging removal of excess/out of date medication
+ Safety netting e.g. Communicating with patiens about clinician concern, providing worsening advice, liasing with carers.

```{r code-plan}

knitr::kable(care_df, caption = "Themes arising from free-text responses relating to care planning for patients having difficulty managing their medication", format = format)

```
