---
output: html_document
editor_options: 
  chunk_output_type: console
---
# Results {-}

```{r results, echo=F, message=F, warning=F}
  # Use pandoc for Word documents
  format="pandoc"

knitr::opts_chunk$set(echo = F, message = F, warning = F, cache = F, fig.align = 'center', out.width = '90%', fig.width = 10)

library(bookdown)
library(tidyverse)
library(lubridate)
library(tableone)
library(readxl)
library(yardstick)


questions <- readRDS('data/orig_col_names.rds')

df <- readRDS('data/df.rds') %>%
  mutate_at(vars(starts_with("freq_fall_"), "prop_non_convey_diff_meds"), as.numeric) %>%
  # Tidy up some values and combine others with
  # small values
  mutate(
    role = case_when(
      role %in% c("cdm", "clinical supervisor", "consultant paramedic", "locality manager", "manager", "frequent caller case officer") ~ "manager",
    grepl("student", role) ~ "student paramedic",
    role %in% c("eca", "emergency care assistant") ~ "emergency care assistant",
    TRUE ~ role
    ),
    cmr_refer = case_when(
      grepl("know", cmr_refer) ~ "unsure",
      TRUE ~ cmr_refer
    ),
    cmr_yes_no = ifelse(grepl("yes", cmr_refer), "yes", "no/unsure"),
    # Sort cmr referral importance as factor
    imp_cmr_refer_option = ordered(imp_cmr_refer_option, levels = c("very important", "important", "neutral", "unimportant", "very unimportant")),
    freq_falls_over65 = factor(freq_falls_over65, levels = c("more than once a shift", "once a shift", "once a week", "once a month")),
  )


df1 <- df %>%
  rename(
    `respondent role` = role,
    `full-time/part-time` = freq_ops,
    # Note use of bang-bang and :=
    !!questions[4]  := freq_falls_over65,
    !!questions[5]  := freq_fall_nonconvey,
    !!questions[6]  := freq_fall_refer,
    !!questions[7]  := freq_fall_gp,
    !!questions[13] := prop_non_convey_diff_meds,
    !!questions[15] := cmr_refer,
    !!questions[16] := imp_cmr_refer_option
  )

vars <- df1 %>% select("respondent role", "full-time/part-time",  questions[4:7], questions[c(13,15:16)]) %>% colnames()

summary_table <- CreateTableOne(
  vars = vars,
  strata = "cmr_yes_no",
  data = df1,
  test = F,
  factorVars = c("respondent role", "full-time/part-time", questions[4],  questions[15], questions[16]),
  includeNA = T,
  addOverall = T
)

nonnormal <- questions[c(4:7,13)]

cmr_summary = df1 %>% count(cmr_yes_no)


# Process free text response coding


struggle_df <- df %>%
  dplyr::select(starts_with("struggle_theme")) %>%
  mutate(
    id = row_number()
  ) %>%
  pivot_longer(cols = starts_with("struggle"), 
               names_to=c("rank", "person"), 
               names_pattern = "struggle_theme_?(.*)\\.(.*)",
               values_to = "theme") %>%
  filter(!is.na(theme)) %>%
  group_by(id) %>%
  summarise(
    "observation of living situation" = sum(theme == "observation of living situation"),
    "observation of patient" = sum(theme == "observation of patient"),
    "patient / carer discussion / disclosure" = sum(theme == "patient / carer discussion / disclosure"),
    "patient clinical presentation" = sum(theme == "patient clinical presentation"),
  ) %>%
  pivot_longer(cols = -id, names_to = "theme", values_to = "value") %>%
  filter(value == 2) %>%
  count(theme, sort = T)

care_df <- df %>%
  dplyr::select(starts_with("care_plan_theme")) %>%
  mutate(
    id = row_number()
  ) %>%
  pivot_longer(cols = starts_with("care"), 
               names_to=c("rank", "person"), 
               names_pattern = "care_plan_theme_?(.*)\\.(.*)",
               values_to = "theme") %>%
  filter(!is.na(theme)) %>%
  group_by(id) %>%
  summarise(
    "discuss and confirm" = sum(theme == "discuss and confirm"),
    "immediate mitigation" = sum(theme == "immediate mitigation"),
    "referral" = sum(theme == "referral"),
    "safety net" = sum(theme == "safety net"),
  ) %>%
  pivot_longer(cols = -id, names_to = "theme", values_to = "value") %>%
  filter(value == 2) %>%
  count(theme, sort = T)

```

There were `r df1 %>% count() %>% pull(n)` responses to the survey, including `r cmr_summary$n[2]`/`r df1 %>% count() %>% pull(n)` (`r round((cmr_summary$n[2]/df1 %>% count() %>% pull(n))*100, 1)`%) from clinicians who had made a CMR referral (Table \@ref(tab:summarytable)).

Most FT
Most experienced patient falling at least once a shift or higher
Responses relating to falling and referrals similar between groups except:
Higher percentage of aptients not conveyed 40 vs 50
Diff with meds 30 vs 50

Importance of CMR referrak: Similar between groups 85.1% vs 88.9%

The highest weighted mean scores for risk factors were
Patient not taking medication as prescribed
Unused medicines around the home

Also these two had highest number of responses.

There was no correlation between Likert score and the role or FT/PT status of respondent.





```{r summarytable}

kableone(print(summary_table, showAllLevels = T, nonnormal = nonnormal), format = format, caption = "Summary of survey responses")

```

## Primary outcome {-}




```{r rank}

rank_df <- df %>%
  select(id, risk_factors_diff_meds) %>%
  # Split character vector into list and then put each row of the list on a new dataframe row
  unnest(y = str_split(risk_factors_diff_meds, "\r\n\\s?", simplify = F)) %>% select(id, y) %>%
  # Separate the number (rank) from the risk factor (item)
  separate(col="y", into=c("rank", "item"), sep = "(?<=[\\d+])\\s?") %>%
  filter(
    # Only going to look at top 5 since likely people got bored after
    # dragging and dropping 5 risk factors around the screen
    rank <= 5,
    # Rank 10 was split into 1 and 0. Not a problem since not including it, but it needs removing
    item != 0
  ) %>%
  mutate(
    item = str_replace(item, "\\r?\\s?\\d+", ""),
    item = ifelse(grepl("can", item), "patient cannot recall all their prescribed medicines", item)
  )

totals_df <- rank_df %>%
  count(item, rank) %>%
  group_by(item) %>%
  summarise(
    tot_n = sum(n),
    rank1 = sum(n[rank == "1"], na.rm = T),
    rank2 = sum(n[rank == "2"], na.rm = T),
    rank3 = sum(n[rank == "3"], na.rm = T),
    rank4 = sum(n[rank == "4"], na.rm = T),
    rank5 = sum(n[rank == "5"], na.rm = T),
    total = 5*first(n[rank == "1"], default = 0) + 4*first(n[rank == "2"], default = 0) + 3*first(n[rank == "3"], default = 0) + 2*first(n[rank == "4"], default = 0) + first(n[rank == "5"], default = 0),
    wght_mean = round(total/tot_n,1)
  ) %>%
  arrange(desc(wght_mean)) %>%
  select(-total) %>%
  select(item, rank1, rank2, rank3, rank4, rank5, tot_n, wght_mean)

colnames(totals_df) <- c("Risk factor",  "1st", "2nd", "3rd", "4th", "5th","total number of responses", "weighted mean")


```


```{r rank-score}

knitr::kable(totals_df, caption = "Risk factors for patients having difficulty managing their medication ordered by weight mean", format = format)

```

For the primary outcome see Table \@ref(tab:rank)).

## Secondary outcome {-}

Descriptive statistics will be used to describe the perceived proportion of falls patients who may have difficulty managing medicines by respondents.  Descriptive statistics will also be used to summarise the value respondents place on a CMR referral pathway, which will be reported on a 5-point Likert scale. Finally, the correlation between the 5-point Likert scale of the value of a CMR referral pathway and respondent demographic details (current role, length of service and frequency of operational duties) will be determine using ordinal logistic regression to account for the ordinal nature of the Likert scale. 

```{r}

library(MASS)

df2 <- df %>%
  dplyr::select(role, freq_ops, cmr_yes_no, imp_cmr_refer_option, freq_falls_over65, freq_fall_refer) %>%
  mutate(paramedic = ifelse(grepl("paramedic", role), 1, 0))

#fit <- polr(imp_cmr_refer_option ~ paramedic + freq_ops, data = df2)

fit <- polr(imp_cmr_refer_option ~ relevel(as.factor(role), ref = "paramedic") + freq_ops, data = df2, Hess = T)

olr_result <- tidy(fit, exponentiate = T, conf.int = T, p.values = T)

olr_res2 <- olr_result %>% 
   mutate_if(is.double, round,2) %>% 
  filter(coef.type == "coefficient") %>% 
  mutate(
    `95% CI` = paste0(conf.low,"--", conf.high),
    term = case_when(
      # https://stackoverflow.com/questions/3872070/how-to-force-r-to-use-a-specified-factor-level-as-reference-in-a-regression
      #https://stackoverflow.com/a/32767436/3650230
      
      grepl("relevel", term) ~ gsub(".*?)", "", str_replace(term, " \\(.*\\)", "")),
      TRUE ~ str_replace(term, "freq_ops", "")
    )
  ) %>%
  dplyr::select(term, estimate, `95%CI`)

knitr::kable(olr_res2, caption = "Ordinal regression model between reported importance of CMR referral and respondent role and frequency of operational duties")

#coeffs <- coef(summary(fit))
#p <- pnorm(abs(coeffs[,"t value"]), lower.tail = F) * 2

#cbind(coeffs, "p value" = round(p, 3))

```


```{r code-struggle}

knitr::kable(struggle_df, caption = "Themes arising from free-text responses relating to respondents identifying a patient having difficulty with their medication", format = format)

```


```{r code-plan}

knitr::kable(care_df, caption = "Themes arising from free-text responses relating to care planning for patients having difficulty managing their medication", format = format)

```
